quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-06 paper-quollr.Rmd
Updated application views

```{r, eval=knitr::is_html_output()}
htmltools::browsable(
  htmltools::tagList(
    tags$div(
      id = "fig-limb-model",  # Anchor for referencing
      style = "text-align: center; margin-bottom: 1em;",

      # 2x2 grid layout
      htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr; row-gap: 0px; justify-items: center;",
        trimesh_limb_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis),
        trimesh_limb_best_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis_best)
      ),

      # Caption
      tags$p(
        tags$strong("Figure 6:"), 
        "Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$."
      )
    )
  )
)

>>>>

```{r model-limb-html, eval=knitr::is_html_output(), fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$."}

modellimbfig <- htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr; row-gap: 0px; justify-items: center;",
        trimesh_limb_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis),
        trimesh_limb_best_int,
        htmltools::div(style = "margin-top: 13px;", limb_highd_vis_best)
      )

class(modellimbfig) <- c(class(modellimbfig), "htmlwidget")

modellimbfig
```
